---
title: "2020_R_IAN_larger_app"
author: "Joseph Edgerton"
date: "1/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r install packages}
my_packages <- c("tidyverse", "GGally", "network", "here", "ggimage",
                 "googlesheets4", "sna","gt", "shinyscreenshot", "Rtools", "Rcpp")
install.packages(my_packages, repos = "http://cran.rstudio.com")

```


```{r}
install.packages("devtools")
install.packages("Rtools")
devtools::install_github("andrie/gcalendr")
```


```{r load packages}

library(tidyverse)
library(GGally)
library(network)
library(here)
library(ggimage)
library(googlesheets4)
library(sna)
library(gt)
library(shiny)
library(lubridate)
library(shinyscreenshot)
library(gcalendr)
library(scales)
```


```{r test gcalendar}
calendar_auth("jedgerton@umces.edu")

my_cal_id <- "jedgerton@umces.edu"
events <- calendar_events(my_cal_id, days_in_past = 7, days_in_future = 0)
events

events_clean <- events %>% 
  select(summary, start_datetime, end_datetime) %>% 
  mutate(name = "Joe")

events_clean

```

```{r create time y-axis/table column}

x <- interval(events_clean$start_datetime, events_clean$end_datetime, tz = "US/Eastern")

x_tibble <- tibble(x)
x_tibble
```







```{r}
new_time <- seq(mdy_hms("02/08/2021 06:00:00", tz = "US/Eastern"), mdy_hms("02/08/2021 17:00:00", tz = "US/Eastern"), by = "15 min")

new_time
#time_object <- as_tibble(new_time)

#time_object <- new_time %>% 
#  filter(!(hour(value) > 17)) %>% 
#  filter(!(hour(value) == 17 & minute(value) == 45)) %>% 
#  filter(!(hour(value) == 17 & minute(value) == 30)) %>% 
#  filter(!(hour(value) == 17 & minute(value) == 15))

time_object_table <- int_diff(new_time)

time_object_tibble <- tibble(time_object_table)
  

time_object_tibble <-  time_object_tibble %>% 
  mutate(Joe = "")
time_object_tibble
#while this was a useful exercise to learn more about intervals, I think it's getting too complicated for my purpose

```

```{r}
glimpse(time_object_tibble$time_object_table)
glimpse(x_tibble$x)

```




```{r calendar table test}


time_object_tibble %>%   
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows = (time_object_tibble$time_object_table %within% x_tibble$x)))

#######################################################
#make a fake event coffee call 1 min to 29 min
#findInterval function, which interval falls in another
findInterval(1:8,c(0,3,6))
#second vector, create hour breaks (gCalendar), in the first part put 15-min chunk
?findInterval
floor(-1.5) #other useful functions
ceiling() 
?floor()
integer(1.5) 

round(1.5)
round(0.5)
############################################################


time_object_tibble %>%   
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows = (findInterval(x_tibble$x, time_object_tibble$time_object_table))))




##########################################
time_object_tibble %>%   
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows = lubridate::int_overlaps(time_object_tibble$time_object_table, x_tibble$x)))




########################################################
time_object_tibble %>%   
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows = lubridate::intersect(time_object_tibble$time_object_table, x_tibble$x)))

time_object_tibble$time_object_table %within%  x_tibble$x

lubridate::int_overlaps(time_object_tibble$time_object_table, x_tibble$x)

lubridate::`%within%`(time_object_tibble$time_object_table, x_tibble$x)

#John from aggregate:
#  A nice way to deal with gt() problem: cat(str_wrap(thanks, width = 40), "\n")

```

```{r 1 event}

test_time_intervals <- int_diff(seq(mdy_hms("02/08/2021 06:00:00", tz = "US/Eastern"), mdy_hms("02/08/2021 17:00:00", tz = "US/Eastern"), by = "15 min"))


test_event <- mdy_hms("02/08/2021 09:00:00", tz = "US/Eastern") %--% mdy_hms("02/08/2021 9:30:00", tz = "US/Eastern")

test_event


test_time_intervals %within% test_event 

class(test_time_intervals)

tibble_time_interval <- tibble(test_time_intervals) %>% 
  mutate(Joe = "")

tibble_time_interval

tibble_time_interval %>%   
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows = test_time_intervals %within% test_event))


```


```{r reprex example problem}

test_time_intervals <- int_diff(seq(mdy_hms("02/08/2021 06:00:00", tz = "US/Eastern"), mdy_hms("02/08/2021 17:00:00", tz = "US/Eastern"), by = "15 min"))


test_event <- c(mdy_hms("02/08/2021 09:00:00", tz = "US/Eastern") %--% mdy_hms("02/08/2021 9:30:00", tz = "US/Eastern"), mdy_hms("02/08/2021 10:00:00", tz = "US/Eastern") %--% mdy_hms("02/08/2021 11:30:00", tz = "US/Eastern"))

test_event


test_time_intervals %within% test_event 

class(test_time_intervals)

tibble_time_interval <- tibble(test_time_intervals) %>% 
  mutate(Joe = "")

tibble_time_interval

tibble_time_interval %>%   
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows = test_time_intervals %within% test_event))


```


Ok, the problem with lubridate is it can't apply the search to every 15 minute interval if I'm searching through multiple events, now should try purrr.

```{r reprex example solution}
test_time_intervals <- int_diff(seq(mdy_hms("02/08/2021 06:00:00", tz = "US/Eastern"), mdy_hms("02/08/2021 17:00:00", tz = "US/Eastern"), by = "15 min"))

test_time_intervals

test_event <- c(mdy_hms("02/08/2021 09:00:00", tz = "US/Eastern") %--% mdy_hms("02/08/2021 9:30:00", tz = "US/Eastern"), mdy_hms("02/08/2021 10:00:00", tz = "US/Eastern") %--% mdy_hms("02/08/2021 11:30:00", tz = "US/Eastern"))

test_event

?seq


events_from_calendar <- function(x){
  (x %within% test_event)
}


my_tibble <- tibble(intervals = test_time_intervals,
                    interval_check = map(test_time_intervals, events_from_calendar),
                    Joe = "")


t <- my_tibble %>% 
  unnest_wider(interval_check)


as.logical(TRUE + TRUE)
as.logical(FALSE + TRUE)
as.logical(FALSE + FALSE)


t1 <- my_tibble %>% 
  unnest_wider(interval_check) %>% 
  mutate(interval_combine_check = as.logical(...1 + ...2))

t1
#now to account for many columns
t2 <- my_tibble %>% 
  unnest_wider(interval_check) %>% 
  rowwise() %>% 
  mutate(final_sum = as.logical(sum(c_across(cols = tidyselect::starts_with("...")))))
                                                                


t2 %>%  
  select(intervals, Joe) %>% 
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows =  t2$final_sum == TRUE))


#new idea
use Vectorize(a, !b) -> create version, go back to correct syntax/look up


**Vectorize**

vect_within <- Vectorize(function(a,b) {a %within% b}, "a")


#check out function

new(a,b){
  
}

```

```{r getting real data from 1 user to work}

test_time_intervals <- int_diff(seq(mdy_hms("02/15/2021 06:00:00", tz = "US/Eastern"), mdy_hms("02/15/2021 17:00:00", tz = "US/Eastern"), by = "15 min"))


test_event <- c(mdy_hms("02/08/2021 09:00:00", tz = "US/Eastern") %--% mdy_hms("02/08/2021 9:30:00", tz = "US/Eastern"), mdy_hms("02/08/2021 10:00:00", tz = "US/Eastern") %--% mdy_hms("02/08/2021 11:30:00", tz = "US/Eastern"))

#this is the default at the moment, need to work with real data and expandable options

my_cal_id <- "jedgerton@umces.edu"
events_one <- calendar_events(my_cal_id, days_in_past = 0, days_in_future = 7)
events_one

events_clean_one <- events_one %>% 
  select(summary, start_datetime, end_datetime) %>% 
  mutate(name = "Joe")

events_clean_one



events

new_events_one <- events_one %>% 
  select(start_datetime, end_datetime,start_timezone, end_timezone)


new_events_timezone_one <- new_events_one %>% 
  rowwise() %>% 
  mutate(across(.cols = c(start_timezone, end_timezone),
                .fns = ~(case_when(is.na(.x) == TRUE ~ "America/New_York", #setting NY default if #NA
                                   is.na(.x) == FALSE ~ .x)))) %>% 
  mutate(start_datetime = with_tz(start_datetime, tz = start_timezone)) %>% 
  mutate(end_datetime = with_tz(end_datetime, tz = end_timezone)) %>% 
  mutate(start_eastern_converted = with_tz(start_datetime, tz = "US/EASTERN")) %>%
  mutate(end_eastern_converted = with_tz(end_datetime, tz = "US/EASTERN")) %>% 
  select(start_eastern_converted, end_eastern_converted)

new_events_timezone_one

final_intervals_one <- interval(new_events_timezone_one$start_eastern_converted,
                          new_events_timezone_one$end_eastern_converted,
                          tz = "US/EASTERN")
events
new_events_timezone
final_intervals
#fill_in_na_time <- function(x){
#  if (is.na(x)) return (America/New_York)
#}

#p <- fill_in_na_time(new_events$start_timezone)


final_events_from_calendar <- function(x){
  (x %within% final_intervals_one)
}


my_final_tibble <- tibble(intervals = test_time_intervals,
                    interval_check = map(test_time_intervals, final_events_from_calendar),
                    Joe = "")


t3 <- my_final_tibble %>% 
  unnest_wider(interval_check) %>% 
  rowwise() %>% 
  mutate(final_sum = as.logical(sum(c_across(cols = tidyselect::starts_with("...")))))
                                                                


t3 %>%  
  select(intervals, Joe) %>% 
  gt() %>% 
  tab_style(
    style = cell_fill(color = "cyan"),
    locations = cells_body(
      columns = vars(Joe),
      rows =  t3$final_sum == TRUE))

t3


#what the hell, need to investigate more on this is sooo messed up
?gcalendr::calendar_events()


#maybe I need to specify now = Sys.time()? IDK

```





#potentially UTC issue
#find way to tell computer to use the appropriate time
#tell PC clock (windows) to set time to California (PST)
#find approprtiate conversion from UTC









###Other parts of app: Stress graph

```{r stress graphs}

scales::viridis_pal()(5)
#[1] "#440154FF" "#3B528BFF" "#21908CFF" "#5DC863FF" "#FDE725FF"


stress_tibble <- tibble(joe = 1, dylan = 7, alex = 18)

stress_tibble_color <- stress_tibble %>% 
  mutate(across(.cols = everything(), .fns = ~(case_when(.x %in% 0:4 ~ "#440154FF",
                                                         .x %in% 5:8 ~"#3B528BFF",
                                                         .x %in% 9:12 ~ "#21908CFF",
                                                         .x %in% 13:16 ~ "#5DC863FF",
                                                         .x %in% 17:20 ~ "#FDE725FF"))))

stress_tibble_color


#maybe use curvature -1, -0.5, 0, 0.5, 1 and write funciton to occur when the different colors occur

#I think these curvature settings have enough differentiation to use


p <- ggplot()
p1 <- p + geom_point(aes(x = 10, y = 10), size = 100, shape = 21, fill = stress_tibble_color$joe) +
  geom_point(aes(x = 8.5, y = 15), size = 10, shape = 21, fill = "white") +
  geom_point(aes(x = 11.5, y = 15), size = 10, shape = 21, fill = "white") +
  geom_curve(aes(x = 8.5, y = 8, xend = 11.5, yend = 8), curvature = -1, size = 5,
             color = "white", lineend = "round") +
  
  xlim(c(0,20)) + ylim(c(0,20))

p1

#Use separate plots for everyone, in shiny, use 

```










































###Junk


```{r testing junk}
time <- mdy_hms("1/29/2021 06:00:00") %--% mdy_hms("2/03/2021 17:00:00")

time <- as.interval(time)

time <- interval(mdy_hms("1/18/2021 06:00:00"), mdy_hms("1/22/2021 17:00:00"))

dates <- time + hours(1:25)

?hours

int_diff(dates)
```



May be easier to do this with a graph (since continuous, vs. discrete table)

```{r try continous graph instead}

new_events_clean <- events_clean %>%
  mutate(start_datetime = as.character(start_datetime)) %>% 
  mutate(end_datetime = as.character(end_datetime)) %>% 
  separate(start_datetime, into = c("date_s", "time_s"), sep = "\\s") %>% 
  separate(end_datetime, into = c("date_e", "time_e"), sep = "\\s") %>% 
  mutate(across(.cols = c(date_s, date_e), .fns = as_date)) %>% 
  mutate(across(.cols = c(time_s, time_e), .fns = hms))

new_events_clean

p <- ggplot(data = new_events_clean, aes(x = person))
p1 <- p + geom_rect(aes(xmin = person, xmax = person, ymin =time_e, ymax = time_s, fill = person)) + scale_y_time(breaks = date_breaks("1 hour"))

p1

?geom_rect()

#nope, too aesthetically busy to be specific, I don't think this will work as a graph, going to use gt table
```









